MS_CNuptake.Rmd

### 2022-09-08 MS_CNuptake.Rmd
update

@@

#ndep check - BP adding ndep - significant
BP_dataset_ndep <- na.omit(NPP_forest[,c("tnpp_a","ndep_a","age_a","fAPAR_a","CNrt_a","Tg_a","PPFD_a","vpd_a","site_a")])
dim(BP_dataset_ndep)
stepwise(BP_dataset_ndep,"tnpp_a")[[1]]
stepwise(BP_dataset_ndep,"tnpp_a")[[3]]
bp_model_ndep <- (lmer(tnpp_a~Tg_a+fAPAR_a+ndep_a+CNrt_a+age_a+(1|site_a),data=BP_dataset_ndep))
summary(bp_model_ndep)
r.squaredGLMM(bp_model_ndep)
```

@@

#anpp_tnpp_dataset <- na.omit(NPP_forest[,c("anpp_tnpp_a","obs_age_a","observedfAPAR_a","soilCN_a","Tg_a","PPFD_a","vpd_a","site_a")])
#dim(anpp_tnpp_dataset)
#model2 <- stepwise(anpp_tnpp_dataset,"anpp_tnpp_a")
#model2[[1]]
#model2[[2]]
#anpp_tnpp_model <- (lmer(anpp_tnpp_a~soilCN_a+obs_age_a+observedfAPAR_a+(1|site_a),data=anpp_tnpp_dataset))
#summary(anpp_tnpp_model)

@@

vif_anpp_tnpp <- vif((lmer(anpp_tnpp_a~Tg_a+fAPAR_a+PPFD_a+CNrt_a+age_a+vpd_a+(1|site_a),data=anpp_tnpp_dataset2)))
```

### Leaf NPP
```{r}
#with age, but age should be removed since it shows higher AIC and lower R2
anpp_leafnpp_dataset_age <- na.omit(NPP_forest[,c("anpp_leafnpp_a","age_a","fAPAR_a","CNrt_a","Tg_a","PPFD_a","vpd_a","site_a")])
model3a <- stepwise(anpp_leafnpp_dataset_age,"anpp_leafnpp_a")
model3a[[1]]
model3a[[2]]
model3a[[3]]
test <- (lmer(anpp_leafnpp_a~age_a+PPFD_a+vpd_a+(1|site_a),data=anpp_leafnpp_dataset_age)) 
summary(test)

#AIC: 1359
r.squaredGLMM(test)
AIC(test)
BIC(test)

#AIC: 1351
r.squaredGLMM(lmer(anpp_leafnpp_a~Tg_a+PPFD_a+vpd_a+(1|site_a),data=anpp_leafnpp_dataset_age)) 
AIC(lmer(anpp_leafnpp_a~Tg_a+PPFD_a+vpd_a+(1|site_a),data=anpp_leafnpp_dataset_age)) 
BIC(lmer(anpp_leafnpp_a~Tg_a+PPFD_a+vpd_a+(1|site_a),data=anpp_leafnpp_dataset_age))

#AIC: 1343
r.squaredGLMM(lmer(anpp_leafnpp_a~fAPAR_a+PPFD_a+vpd_a+(1|site_a),data=anpp_leafnpp_dataset_age)) 
AIC(lmer(anpp_leafnpp_a~fAPAR_a+PPFD_a+vpd_a+(1|site_a),data=anpp_leafnpp_dataset_age)) 
BIC(lmer(anpp_leafnpp_a~fAPAR_a+PPFD_a+vpd_a+(1|site_a),data=anpp_leafnpp_dataset_age))

@@

@@

@@

### Pre-process data
```{r}
#leaf Nmass
###2. leaf Nmass basing on a site-species model
SP_input <- read.csv(file="~/data/leaf_traits/combined_leaf_traits_updated.csv") #new one
summary(SP_input$C_percent)
#median of value of leaf C = 0.47 or 47%

@@

### Forest Wood C:N + grassland leaf and root C/N
```{r warning=FALSE}
# Wood C/N = 100 - as derived median values of TRY database
wood_cn <- read.csv("~/data/CN_wood/wood_cn.csv")
wood_cn_sitemean <- aggregate(wood_cn,by=list(wood_cn$lon,wood_cn$lat), FUN=mean, na.rm=TRUE) 
summary(wood_cn_sitemean$OrigValueStr)
dim(wood_cn_sitemean)

##2. For Grassland
#leaf c/n model. median = 18. 
#root c/n model median = 41.
#see line 887-888 in Forest_site_org, all derived from "TianDi Grassland", but its BP, ANPP, BNPP data not used in our study
#summary(aggregate(subset(dataset6,pft=="Grassland"),by=list(subset(dataset6,pft=="Grassland")$site), FUN=mean, na.rm=TRUE)$CN_leaf_final)
#summary(aggregate(subset(dataset6,pft=="Grassland")  ,by=list(subset(dataset6,pft=="Grassland")$site), FUN=mean, na.rm=TRUE)$CN_root_final)
```

@@

NPP_forest$pred_leafnc <- (summary(n1)$coefficients[1,1]/0.47) + 
  (summary(n1)$coefficients[2,1]/0.47) * NPP_forest$vcmax25/NPP_forest$LMA

@@

NPP_forest$pred_wnf <- NPP_forest$pred_wnpp/100
NPP_forest$pred_bnf <- NPP_forest$pred_bnpp/94

@@

# what are these numbers (0.49, 18, 41, ...)
# 0.49 as derived from anpp/tnpp ratio (fixed in grassland)
summary((lm(anpp_a~-1+tnpp_a,data=grassland_sitemean)))

#For 18 and 41 they are fixed values of leaf and root C/N, as derived from "Tian Di Grassland"
#see line 402-403
#see line 899 in https://github.com/yunkepeng/nimpl_sofun_inputs_final/blob/main/submission_newphytol/preprocessing/Forest_site_orig.R, 
#data all derived from "TianDi Grassland", but their BP, ANPP, BNPP data not used in our study
#summary(aggregate(subset(dataset6,pft=="Grassland"),by=list(subset(dataset6,pft=="Grassland")$site), FUN=mean, na.rm=TRUE)$CN_leaf_final)
#summary(aggregate(subset(dataset6,pft=="Grassland"),by=list(subset(dataset6,pft=="Grassland")$site), FUN=mean, na.rm=TRUE)$CN_root_final)

NPP_grassland$grassland_pred_anpp <- NPP_grassland$grassland_pred_npp * 0.49
NPP_grassland$grassland_pred_lnf <- NPP_grassland$grassland_pred_anpp/18
NPP_grassland$grassland_pred_bnpp <- NPP_grassland$grassland_pred_npp - NPP_grassland$grassland_pred_anpp
NPP_grassland$grassland_pred_bnf <- NPP_grassland$grassland_pred_bnpp/41
NPP_grassland$grassland_pred_nuptake <- NPP_grassland$grassland_pred_lnf*(1-0.69)+NPP_grassland$grassland_pred_bnf

@@

###3. calculate weighted-sum
#firstly - filter na points - so that all output map has same numbers of NA.
# all_predictors <- as.data.frame(cbind(Tg$Tg,PPFD$PPFD,vpd$vpd,
#                                       fAPAR$fAPAR,age$age,
#                                       CNrt$CNrt,LMA$LMA,vcmax25_df$vcmax25))

@@

#represent grids when stand-age is especially in NA, but others are fine
names(all_predictors) <- c("Tg","PPFD","vpd","fAPAR","age","CNrt","LMA","vcmax25","available_grid")
all_predictors$lon <- vcmax25_df$lon
all_predictors$lat <- vcmax25_df$lat
summary(all_predictors)

#final calculation - now divide into forest, grassland and pft
#available_grid2 here was used as a list of data to identify if a grid is available (=1) or any prediction fields shown as NA

#bp_model,anpp_tnpp_model,anpp_leafnpp_model,bp_grass_model,0.49/0.51,n1,nre_model

@@

leafnc_f <- (summary(n1)$coefficients[1,1]/0.47) + 
  (summary(n1)$coefficients[2,1]/0.47) * vcmax25_df$vcmax25/LMA$LMA

@@

lnf_f <- (1-nre_f)* leafnc_f * lnpp_f
wnf_f <- wnpp_f/100
#100 is constant wood c/n
bnf_f <- bnpp_f/94
#94 is constant root c/n
nuptake_f <- lnf_f + wnf_f + bnf_f

@@

# what are these numbers (0.49, 1/18, 0.69, ...)
# 0.49, as explained above - are anpp/npp ratio in grassland (see line 552)
# 18, as explained above - are constant leaf C/N (see line 554)
# 0.69, as explained in above line - are constant NRE see line 442)

anpp_g <- npp_g* 0.49
bnpp_g <- npp_g-anpp_g

leafnc_g <- 1/18

nre_g <- 0.69

@@

bnf_g <- bnpp_g *(1/41)
#41 is constant root c/n
nuptake_g <- lnf_g + bnf_g

@@

#CLM
#CLM_fNup <- as.data.frame(nc_to_df(read_nc_onefile("~/data/trendy/v8/CLM5.0_S2_fNup_ANN_mean.nc"), varnam = "fNup")) 
#this product is confusing (1) unit needs /1000 to get gn/m2/year? (2)still many values very high
CLM_GPP <- as.data.frame(nc_to_df(read_nc_onefile("~/data/trendy/v8/CLM5.0_S2_gpp_ANN_mean.nc"), varnam = "gpp"))
CLM_GPP$lon[CLM_GPP$lon>180] <- CLM_GPP$lon[CLM_GPP$lon>180]-360
CLM_NPP <- as.data.frame(nc_to_df(read_nc_onefile("~/data/trendy/v8/CLM5.0_S2_npp_ANN_mean.nc"), varnam = "npp"))
CLM_NPP$lon[CLM_NPP$lon>180] <- CLM_NPP$lon[CLM_NPP$lon>180]-360

@@

```{r warning=FALSE}
#all_maps
not_used <- list(CLASS_GPP,CLASS_NPP,CLM_GPP,CLM_NPP,JSBACH_fNup,JSBACH_GPP,JSBACH_NPP)

@@

#CLM has some problem here for coordinates - need convert # CLM_NPP$lon[CLM_NPP$lon>180] <- CLM_NPP$lon[CLM_NPP$lon>180]-360
sitemean2 <- sitemean
sitemean2$lon[sitemean2$lon<0] <- sitemean2$lon[sitemean2$lon<0]+360
sp_sites2 <- SpatialPoints(sitemean2) # only select lon and lat
CLM_NPP <- (raster::extract(raster_CLM_npp, sp_sites2, sp = TRUE) %>% as_tibble() %>% right_join(sitemean2, by = c("lon", "lat")))[,1]

@@

## Nuptake or NUE vs. all predictors
```{r, warning=FALSE}
#nue and nuptake relation
#also, our simulations
NPP_grassland_remove <- NPP_grassland
forest_NUE <- NPP_forest[,c("lon","lat","pred_nuptake","pred_npp","age_a","Tg_a","PPFD_a","vpd_a","fAPAR_a",
                            "CNrt_a","LMA_a","vcmax25_a")]
grassland_NUE <- NPP_grassland_remove[,c("lon","lat","grassland_pred_nuptake","grassland_pred_npp","age_a","Tg_a","PPFD_a","vpd_a","fAPAR_a",
                                         "CNrt_a","LMA_a","vcmax25_a")]
names(grassland_NUE) <- c("lon","lat","pred_nuptake","pred_npp","age_a","Tg_a","PPFD_a","vpd_a","fAPAR_a",
                          "CNrt_a","LMA_a","vcmax25_a")
nue_allplots <- as.data.frame(rbind(forest_NUE,grassland_NUE))
nue_allplots$nue <-nue_allplots$pred_npp/nue_allplots$pred_nuptake

@@

## Nuptake or NUE vs. all predictors

@@

#leaf n/c - ALREADY checked that inputted vcmax25_df + LMA calculated from (1) fortran and (2) R for predicting leaf n/c, could output the same prediction for leaf n/c Please note! using a.vcmax25.nc rather than annualvcmax25.nc. See difference in: https://www.notion.so/computationales/annualvcmax25-vs-a-vcmax25-282bddd63bba4d7b9cfcc75805b45964
n1 <- lmer(nmass_a~vcmax25_lma_a + (1|sitename_a)+(1|species_a))
mod_leafnc_uncertainty <-summary(n1)$sigma/0.47
summary(mod_leafnc_uncertainty)

@@

### Wood N flux
```{r}
#now, uncertainty of wood n uptake flux (assuming wood c/n is a constant = 100)
uncertainty_wnf <- uncertainty_wnpp/100
summary(uncertainty_wnf/wnf_f)

@@

### Root N flux
```{r}
#root N flux = uncertainty of bnpp * root N/C
uncertainty_bnf <- uncertainty_bnpp/94

@@

#grassland
uncertainty_npp_grassland
uncertainty_anpp_grassland <- uncertainty_npp_grassland*0.49
uncertainty_bnpp_grassland <- uncertainty_npp_grassland*0.51
uncertainty_lnf_grassland <- uncertainty_npp_grassland*0.49*(1-0.69)/18
uncertainty_bnf_grassland <- uncertainty_npp_grassland*0.51/41
uncertainty_nuptake_grassland <- sqrt(uncertainty_lnf_grassland^2 + uncertainty_bnf_grassland^2)
```

@@

#final nue - calculated from final results
#forest nue:
(55.74/0.79) 
#grassland nue:
(16.37/0.34)
#total nue:
(72.06/1.13) 
#forest nue uncertainty:
(55.74/0.79) * sqrt( (10.62/55.74)^2 +(0.23/0.79)^2)
#grassland nue uncertainty:
(16.32/0.34) * sqrt( (9.65/16.32)^2 +(0.15/0.34)^2)
#pft
(72.06/1.13) * sqrt( (14.35/72.06)^2 +(0.27/1.13)^2)
```

>>>>

Constant setting - copied this to cal_nue.R when making change
```{r}

#set leaf Cmass, wood C/N, root C/N and wood tissue percentage in forest as constant
#see below code
leaf_c_forest <- 0.47

#set wood and root ratio, and wood tissue percentage
wood_cn_forest <- 319 #(from mean values of Zhang et al. 2019 GCB doi: 10.1111/gcb.14973)
root_cn_forest <- 94 # see below code
wood_tissue_percentage <- 1 #0.272
###

#For 18 and 41 they are fixed values of leaf and root C/N, as derived from "Tian Di Grassland"
#see line 884 and 885 in preparation code: https://github.com/yunkepeng/nimpl_sofun_inputs_final/blob/main/submission_newphytol/preprocessing/Forest_site_orig.R, 
#data all derived from "TianDi Grassland", but their BP, ANPP, BNPP data not used in our study
#summary(aggregate(subset(dataset6,pft=="Grassland"),by=list(subset(dataset6,pft=="Grassland")$site), FUN=mean, na.rm=TRUE)$CN_leaf_final)
#summary(aggregate(subset(dataset6,pft=="Grassland"),by=list(subset(dataset6,pft=="Grassland")$site), FUN=mean, na.rm=TRUE)$CN_root_final)
leaf_cn_grassland <- 18

root_cn_grassland <- 41

#nre constant at grassland - see below code - median values of literature Du and Deng
nre_grassland_constant <- 0.69

#applying null model of anpp/bp - see below code
anpp_bp_grassland <- 0.50

@@

#ndep check - BP adding ndep - significant
BP_dataset_ndep <- na.omit(NPP_forest[,c("tnpp_a","ndep_a","age_a","fAPAR_a","CNrt_a","Tg_a","PPFD_a","vpd_a","site_a")])
dim(BP_dataset_ndep)
stepwise(BP_dataset_ndep,"tnpp_a")[[1]]
stepwise(BP_dataset_ndep,"tnpp_a")[[3]]
bp_model_ndep <- (lmer(tnpp_a~Tg_a+fAPAR_a+ndep_a+CNrt_a+age_a+(1|site_a),data=BP_dataset_ndep))
summary(bp_model_ndep)
r.squaredGLMM(bp_model_ndep)

#latitude check - check if it can replace Tg as a good predictor?
NPP_forest$lat_abs <- abs(NPP_forest$lat)
BP_dataset_lat <- na.omit(NPP_forest[,c("tnpp_a","lat_abs","age_a","fAPAR_a","CNrt_a","Tg_a","PPFD_a","vpd_a","site_a")])
dim(BP_dataset_lat)
stepwise(BP_dataset_lat,"tnpp_a")[[1]]
stepwise(BP_dataset_lat,"tnpp_a")[[3]]
#lat will not help us to improve the model!

@@

#check significance at iteration
summary((lmer(tnpp_a~Tg_a+(1|site_a),data=BP_dataset2)))
summary((lmer(tnpp_a~Tg_a+fAPAR_a+(1|site_a),data=BP_dataset2)))
summary((lmer(tnpp_a~Tg_a+fAPAR_a+age_a+(1|site_a),data=BP_dataset2)))
summary((lmer(tnpp_a~Tg_a+fAPAR_a+age_a+CNrt_a+(1|site_a),data=BP_dataset2)))
summary((lmer(tnpp_a~Tg_a+fAPAR_a+PPFD_a+CNrt_a+age_a+(1|site_a),data=BP_dataset2)))
summary((lmer(tnpp_a~Tg_a+fAPAR_a+PPFD_a+CNrt_a+age_a+vpd_a+(1|site_a),data=BP_dataset2)))

@@

vif_anpp_tnpp <- vif((lmer(anpp_tnpp_a~Tg_a+fAPAR_a+PPFD_a+CNrt_a+age_a+vpd_a+(1|site_a),data=anpp_tnpp_dataset2)))

#check significance at iteration
summary(lmer(anpp_tnpp_a~CNrt_a+(1|site_a),data=anpp_tnpp_dataset2))
summary(lmer(anpp_tnpp_a~CNrt_a+PPFD_a+(1|site_a),data=anpp_tnpp_dataset2))
summary(lmer(anpp_tnpp_a~CNrt_a+PPFD_a+Tg_a+(1|site_a),data=anpp_tnpp_dataset2))
summary(lmer(anpp_tnpp_a~CNrt_a+PPFD_a+Tg_a+age_a+(1|site_a),data=anpp_tnpp_dataset2))
summary(lmer(anpp_tnpp_a~CNrt_a+PPFD_a+Tg_a+age_a+vpd_a+(1|site_a),data=anpp_tnpp_dataset2))
summary(lmer(anpp_tnpp_a~CNrt_a+PPFD_a+Tg_a+age_a+vpd_a+fAPAR_a+(1|site_a),data=anpp_tnpp_dataset2))

### Leaf NPP
```{r}
#with age, but age should be removed since it shows higher AIC and lower R2
anpp_leafnpp_dataset_age <- na.omit(NPP_forest[,c("anpp_leafnpp_a","age_a","fAPAR_a","CNrt_a","Tg_a","PPFD_a","vpd_a","site_a")])
model3a <- stepwise(anpp_leafnpp_dataset_age,"anpp_leafnpp_a")
model3a[[1]]
model3a[[2]]
model3a[[3]]

#check significance at iteration
summary(lmer(anpp_leafnpp_a~age_a+(1|site_a),data=anpp_leafnpp_dataset_age))
summary(lmer(anpp_leafnpp_a~age_a+PPFD_a+(1|site_a),data=anpp_leafnpp_dataset_age))
summary(lmer(anpp_leafnpp_a~age_a+PPFD_a+vpd_a+(1|site_a),data=anpp_leafnpp_dataset_age)) 
summary(lmer(anpp_leafnpp_a~age_a+PPFD_a+vpd_a+Tg_a+(1|site_a),data=anpp_leafnpp_dataset_age)) # non-sigificant in age, so age should be removed
summary(lmer(anpp_leafnpp_a~age_a+PPFD_a+vpd_a+Tg_a+fAPAR_a+(1|site_a),data=anpp_leafnpp_dataset_age))
summary(lmer(anpp_leafnpp_a~age_a+PPFD_a+vpd_a+Tg_a+fAPAR_a+CNrt_a+(1|site_a),data=anpp_leafnpp_dataset_age))

@@

#check significance at iteration
summary(lmer(anpp_leafnpp_a~fAPAR_a+(1|site_a),data=anpp_leafnpp_dataset)) 
summary(lmer(anpp_leafnpp_a~fAPAR_a+PPFD_a+(1|site_a),data=anpp_leafnpp_dataset)) 
summary(lmer(anpp_leafnpp_a~fAPAR_a+PPFD_a+vpd_a+(1|site_a),data=anpp_leafnpp_dataset)) 
summary(lmer(anpp_leafnpp_a~fAPAR_a+PPFD_a+vpd_a+CNrt_a+(1|site_a),data=anpp_leafnpp_dataset)) 
summary(lmer(anpp_leafnpp_a~fAPAR_a+PPFD_a+vpd_a+CNrt_a+Tg_a+(1|site_a),data=anpp_leafnpp_dataset))

@@

#check significance at iteration
summary(lm(tnpp_a~Tg_a,data=BP_dataset_grass))
summary(lm(tnpp_a~PPFD_a+Tg_a,data=BP_dataset_grass))
summary(lm(tnpp_a~PPFD_a+Tg_a+vpd_a,data=BP_dataset_grass))
summary(lm(tnpp_a~PPFD_a+Tg_a+vpd_a+fAPAR_a,data=BP_dataset_grass))
summary(lm(tnpp_a~PPFD_a+Tg_a+vpd_a+fAPAR_a+CNrt_a,data=BP_dataset_grass))

@@

### Pre-process data
```{r}
#leaf Nmass
###2. leaf Nmass basing on a site-species model
SP_input <- read.csv(file="~/data/leaf_traits/combined_leaf_traits_updated.csv") #new one
summary(SP_input$C_percent)
dim(subset(SP_input,C_percent>0))
dim(unique(subset(SP_input,C_percent>0)[,c("lon","lat")]))
#median of value of leaf C = 0.47 or 47%

@@

### Forest Wood C:N - not used
```{r warning=FALSE}
# Wood C/N = 100 - as derived median values of TRY database
wood_cn <- read.csv("~/data/CN_wood/wood_cn.csv")
wood_cn_sitemean <- aggregate(wood_cn,by=list(wood_cn$lon,wood_cn$lat), FUN=mean, na.rm=TRUE) 
summary(wood_cn_sitemean$OrigValueStr)
dim(wood_cn_sitemean)

@@

NPP_forest$pred_leafnc <- (summary(n1)$coefficients[1,1]/leaf_c_forest) + 
  (summary(n1)$coefficients[2,1]/leaf_c_forest) * NPP_forest$vcmax25/NPP_forest$LMA

@@

NPP_forest$pred_wnf <- wood_tissue_percentage*NPP_forest$pred_wnpp/wood_cn_forest
NPP_forest$pred_bnf <- NPP_forest$pred_bnpp/root_cn_forest

@@

summary((lm(anpp_a~-1+tnpp_a,data=grassland_sitemean))) #0.49 as constant scalling

NPP_grassland$grassland_pred_anpp <- NPP_grassland$grassland_pred_npp * anpp_bp_grassland
NPP_grassland$grassland_pred_lnf <- NPP_grassland$grassland_pred_anpp/leaf_cn_grassland
NPP_grassland$grassland_pred_bnpp <- NPP_grassland$grassland_pred_npp - NPP_grassland$grassland_pred_anpp
NPP_grassland$grassland_pred_bnf <- NPP_grassland$grassland_pred_bnpp/root_cn_grassland
NPP_grassland$grassland_pred_nuptake <- NPP_grassland$grassland_pred_lnf*(1-nre_grassland_constant)+NPP_grassland$grassland_pred_bnf

@@

###3. calculate weighted-sum
#firstly - filter na points - so that all output map has same numbers of NA.

@@

#add coordinates
names(all_predictors) <- c("Tg","PPFD","vpd","fAPAR","age","CNrt","LMA","vcmax25","available_grid")
all_predictors$lon <- vcmax25_df$lon
all_predictors$lat <- vcmax25_df$lat
summary(all_predictors)

#available_grid2 here was used as a list of data to identify if a grid is available (=1) or any prediction fields shown as NA

@@

leafnc_f <- (summary(n1)$coefficients[1,1]/leaf_c_forest) + 
  (summary(n1)$coefficients[2,1]/leaf_c_forest) * vcmax25_df$vcmax25/LMA$LMA

@@

lnf_f <- (1-nre_f)* leafnc_f * lnpp_f
wnf_f <- wood_tissue_percentage*wnpp_f/wood_cn_forest
#100 is constant wood c/n
bnf_f <- bnpp_f/root_cn_forest
#94 is constant root c/n
nuptake_f <- lnf_f + wnf_f + bnf_f

@@

anpp_g <- npp_g* anpp_bp_grassland
bnpp_g <- npp_g-anpp_g

leafnc_g <- 1/leaf_cn_grassland

nre_g <- nre_grassland_constant

@@

bnf_g <- bnpp_g *(1/root_cn_grassland)
nuptake_g <- lnf_g + bnf_g

@@

#CLM
#CLM_fNup <- as.data.frame(nc_to_df(read_nc_onefile("~/data/trendy/v8/CLM5.0_S2_fNup_ANN_mean.nc"), varnam = "fNup")) 
#this product is confusing (1) unit needs /1000 to get gn/m2/year? (2)still many values very high
#CLM_GPP <- as.data.frame(nc_to_df(read_nc_onefile("~/data/trendy/v8/CLM5.0_S2_gpp_ANN_mean.nc"), varnam = "gpp"))
#CLM_GPP$lon[CLM_GPP$lon>180] <- CLM_GPP$lon[CLM_GPP$lon>180]-360
#CLM_NPP <- as.data.frame(nc_to_df(read_nc_onefile("~/data/trendy/v8/CLM5.0_S2_npp_ANN_mean.nc"), varnam = "npp"))
#CLM_NPP$lon[CLM_NPP$lon>180] <- CLM_NPP$lon[CLM_NPP$lon>180]-360

@@

```{r warning=FALSE}
#all_maps
#not_used <- list(CLASS_GPP,CLASS_NPP,CLM_GPP,CLM_NPP,JSBACH_fNup,JSBACH_GPP,JSBACH_NPP)

@@

#CLM has some problem here for coordinates (ranging from 0 to 360 in lon) - need convert # CLM_NPP$lon[CLM_NPP$lon>180] <- CLM_NPP$lon[CLM_NPP$lon>180]-360
sitemean2 <- sitemean
sitemean2$lon[sitemean2$lon<0] <- sitemean2$lon[sitemean2$lon<0]+360
sp_sites2 <- SpatialPoints(sitemean2) # only select lon and lat
CLM_NPP <- (raster::extract(raster_CLM_npp, sp_sites2, sp = TRUE) %>% as_tibble() %>% right_join(sitemean2, by = c("lon", "lat")))[,1]

@@

## NUE vs. all predictors
```{r, warning=FALSE}
#nue and nuptake relation
#also, our simulations
NPP_grassland_remove <- NPP_grassland
forest_NUE <- NPP_forest[,c("lon","lat","pred_nuptake","pred_npp","age_a","Tg_a","PPFD_a","vpd_a","fAPAR_a",
                            "CNrt_a","LMA_a","vcmax25_a")]
grassland_NUE <- NPP_grassland_remove[,c("lon","lat","grassland_pred_nuptake","grassland_pred_npp","age_a","Tg_a","PPFD_a","vpd_a","fAPAR_a",
                                         "CNrt_a","LMA_a","vcmax25_a")]
names(grassland_NUE) <- c("lon","lat","pred_nuptake","pred_npp","age_a","Tg_a","PPFD_a","vpd_a","fAPAR_a",
                          "CNrt_a","LMA_a","vcmax25_a")
nue_allplots <- as.data.frame(rbind(forest_NUE,grassland_NUE))
nue_allplots$nue <-nue_allplots$pred_npp/nue_allplots$pred_nuptake

@@

## Nuptake vs. all predictors

@@

#leaf n/c - ALREADY checked that inputted vcmax25_df + LMA calculated from (1) fortran and (2) R for predicting leaf n/c, could output the same prediction for leaf n/c Please note! using a.vcmax25.nc rather than annualvcmax25.nc. See difference in: https://www.notion.so/computationales/annualvcmax25-vs-a-vcmax25-282bddd63bba4d7b9cfcc75805b45964
n1 <- lmer(nmass_a~vcmax25_lma_a + (1|sitename_a)+(1|species_a))
mod_leafnc_uncertainty <-summary(n1)$sigma/leaf_c_forest
summary(mod_leafnc_uncertainty)

@@

### Wood N flux
```{r}
#now, uncertainty of wood n uptake flux
uncertainty_wnf <- wood_tissue_percentage*uncertainty_wnpp/wood_cn_forest
summary(uncertainty_wnf/wnf_f)

@@

### Root N flux
```{r}
#root N flux = uncertainty of bnpp * root N/C
uncertainty_bnf <- uncertainty_bnpp/root_cn_forest

@@

#grassland
uncertainty_npp_grassland
uncertainty_anpp_grassland <- uncertainty_npp_grassland*anpp_bp_grassland
uncertainty_bnpp_grassland <- uncertainty_npp_grassland*(1-anpp_bp_grassland)
uncertainty_lnf_grassland <- uncertainty_npp_grassland*anpp_bp_grassland*(1-nre_grassland_constant)/leaf_cn_grassland
uncertainty_bnf_grassland <- uncertainty_npp_grassland*(1-anpp_bp_grassland)/root_cn_grassland
uncertainty_nuptake_grassland <- sqrt(uncertainty_lnf_grassland^2 + uncertainty_bnf_grassland^2)
```

@@

#final nue - calculated from final results
#forest nue:
(55.74/0.61) 
#grassland nue:
(16.36/0.34)
#total nue:
76.01 # as calculated above
#forest nue uncertainty:
(55.74/0.61)  * sqrt( (10.62/55.74)^2 +(0.22/0.61)^2)
#grassland nue uncertainty:
(16.36/0.34) * sqrt( (9.72/16.36)^2 +(0.15/0.34)^2)
#pft
(72.10/0.95) * sqrt( (14.40/72.10)^2 +(0.26/0.95)^2)
```
